Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-23 article.tex
remove dot in acknowledgement
add damien remark

Considering the short delay of communication between neurons and the slow
decay of fluorescence, the second step of our pipeline consists in identifying
neuron spikes -- characterized by high frequencies -- by filtering out low
frequencies through a high-pass filter, resulting in the plot of
Figure \ref{fig:hp_curve}:
\begin{align}
g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i. \label{eq:high-pass-filter}
\end{align}

@@

\section*{Acknowledgments}
A. Joly and G. Louppe are research fellows of
the FNRS, Belgium.  A. Sutera is recipient of
a F.R.I.A. fellowship of F.R.S.-FNRS, Belgium.
This work is supported by PASCAL2 and the IUAP DYSCO, initiated by the
Belgian State, Science Policy Office.

>>>>

\textcolor{red}{DE: la phrase ne veut rien dire}
Considering the short delay of communication between neurons and the slow
decay of fluorescence, the second step of our pipeline consists in identifying
neuron spikes -- characterized by high frequencies -- by filtering out low
frequencies through a high-pass filter, resulting in the plot of
Figure \ref{fig:hp_curve}:
\begin{align}
g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i. \label{eq:high-pass-filter}
\end{align}

@@

\section*{Acknowledgments}
A Joly and G Louppe are research fellows of the FNRS, Belgium.  A Sutera is
recipient of a FRIA fellowship of FRS-FNRS, Belgium. This work is supported by
PASCAL2 and the IUAP DYSCO, initiated by the Belgian State, Science Policy
Office.
